---
title: "STAT13, Lab 1 Key"
author: "(name)"
output:
  html_document: default
  pdf_document: default
---

# 1 Installing R & R Studio
Please install the most recent version of R & RStudio on your computer.
If you do not have a computer, ask a friend or roommate if you can install it on theirs (you can
uninstall it when you are done). As proof of completion, issue this command:

```
system("who", intern=TRUE)
```
or if you are running Windows:
```{r, results='hide'}
system("whoami", intern=TRUE)
```



#  Application of Basic R Rules
## 3 Please use R as a calculator and show how to get the answers for:
3A  
$\frac{36^3}{7^8}$
```{r}
(36^3)/(7^8)
```
3B  
$6833-843$
```{r}
6833-843
```
3C  
$13^{\frac{3}{5}}$
```{r}
13^(3/5)
```
3D  
$6^{\frac{3}{2}}$
```{r}
6^(3/2)
```
3E  
$\frac{6791+2083-296+3359+502-6429+3834}{7}$

```{r}
(6791+2083-296+3359+502-6429+3834)/7
```
## 4 Vectors
#### 4.1A Please create a numeric vector with (any) 10 elements that are not in a sequence.
```{r}
v1 <- c(5,7,6,3,8,1,4,9,2,0)
v1
```
#### 4.1B Please create a numeric vector consisting of the even numbers from 1 to 100.
```{r}
v2 <- seq(2,100,2)
v2
```
#### 4.1C Please write a single line of code that will generate a vector of the form -m^3, -(m-1)^3, ..., -1, 0, 1, (m-1)^3, m^3 for any m.
```{r}
m <- 5
v3 <- seq(-m,m)^3
v3
```
#### 4.1D Using your 10 element numeric vector from part (a), demonstrate how to divide each element by 4 and then square each the resulting values.
```{r}
v1 <- (v1 / 4)^2
v1
```
#### 4.1E Show how to square only the 3rd and 9th elements of your 10 element numeric vector from part A(this can be done with a single line of code, no semi colons allowed). Your final result should have 10, not 2 elements and maintain their original ordering.
```{r}
v1[c(3,9)] <- v1[c(3,9)]^2
v1
```
#### 4.2A Here are four vectors for you to create: A: (2,6,3,4,6,1,2,1,1), B: (2,3,1,1,1,3,5,8,8,7,3), C: (8,8,7,3,3,4,6,6,1,1,1), D: (2,3,1,1,7,7,5,7). Which one has the highest mean?
```{r}
A<-c(2,6,3,4,6,1,2,1,1)
B<-c(2,3,1,1,1,3,5,8,8,7,3)
C<-c(8,8,7,3,3,4,6,6,1,1,1)
D<-c(2,3,1,1,7,7,5,7)

lapply( list(A,B,C,D), mean)
```
Answer is C.
*They're not expected to use lapply. Just for convenience here.  

#### 4.3B Which one has the greatest standard deviation?
```{r}
lapply( list(A,B,C,D), sd)
```
Answer is C.

### 5 Character (String) and Logical Vectors
#### 5A Create a character vector which looks like this when you print it.
```{r echo=FALSE}
v1 <- c("stat","data","compute","schoenberg","homework","awesome","TA")
v1
```
#### 5B Show how to print the only last two elements of the character vector. This requires only one line of code.
```{r}
tail(v1,2)
```

## 6 Data Frames
### 6A Demonstrate that you are able to use the function data() and that you know what a data frame is by finding a built-in dataset. Please identify the dataset.
```{r}
data(sleep)
```
> This dataset shows the effect of two soporific drugs (increase in hours of sleep compared to control) on 10 patients.

### 6B How many observations and how many variables does your data frame have? Use any R function to reveal this information.
```{r}
str(sleep)
```
> This data frame has 20 observations of 3 variables.

### 6C Reading in CSV files: Directly load into R, the file found in http://www.ats.ucla.edu/stat/data/hsb2.csv.
```{r}
dat.csv <- read.csv("http://www.ats.ucla.edu/stat/data/hsb2.csv")
```


