---
title: "Lab_4 Due 25th Oct"
author: "Helen Huang"
date: "10/20/2017"
output: html_document
---

### Question 1
1. Create a boxplot to show people’s desire weight in this data set.
2. Use which() function to drop all desire weights bigger than 250.
3. Conduct a hypothesis test on wtdesire with significance level 0.05:  
    H0: Population mean of wtdesire is equal to 154.4  
    Ha: Population mean of wtdesire is not equal to 154.4  
Please calculate the p value and write down if you can reject H0 in the comments
(after #).
Hint: Use t distribution and try 2*pt(…).

```{r setup, include=TRUE}
#1
dat <- read.csv(file="cdc.csv", header=TRUE, sep=",")
boxplot(dat["wtdesire"])
#2
index = which(dat["wtdesire"] <=250)
dat = dat[index,]
boxplot(dat["wtdesire"])
#3
n = length(dat$wtdesire)
t = (mean(dat$wtdesire)-154.4)/(sd(dat$wtdesire)/sqrt(n))
p = 2*(pt(t, n-1))
#We fail to reject the null hypothesis as there is no evidence against the null hypothesis since p=1.46323686455904, which is way larger than the significance level 0.05.
```

## The following part is optional 

4. Conduct a hypothesis test on wtdesire with significance level 0.05:  
    H0: Population mean of wtdesire is equal to 153.7  
    Ha: Population mean of wtdesire is not equal to 153.7  
Please calculate the p value and write down if you can reject H0 in the comments
(after #).
Hint: Use t distribution and try 2*(1-pt(…)).

```{r 4}
t2 = (mean(dat$wtdesire)-153.7)/(sd(dat$wtdesire)/sqrt(n))
p2 = 2*(1-pt(t2, n-1))
p3 = 2*(pt(-5.07, 59))
#There is strong evidence against the null hypothesis, since the p value is very small, only 0.00012434907449177, way smaller than the significance level 0.05.
```